\subsection{State of the Art}
% Review all of the current experimental evidence pertaining to my area of research
\todo[inline]{Talk quantum electron spin, projective measurement vs non-projective measurement (bloch sphere), about technology behind SETs}
\subsubsection{Quantum Information}
\todo[inline]{Fix this, too much detail on spin}
A quantum computer is composed of quantum bits of information, known as qubits. In the devices manufactured by CQC2T a qubit is created from the physical property of an electron known as spin. Spin is the intrinsic magnetic moment of nano structures, essentially a small magnetic dipole, that can point in any direction in free space. For an electron, you can measure the value of this magnetic moment to be $S = \frac{\hbar}{2}$ (denoted "spin one half"). Despite this freedom of orientation, if you were to measure this spin in an arbitrary orientation, you will always find the spin to be aligned or anti-aligned to the axis of measurement (with some exceptions). For example, if you were to measure in the z-axis you would find the following:
$$S_x = 0; S_y = 0; S_z = \pm\frac{\hbar}{2}$$

Where the sign indicates alignment or anti-alignment.
However, if you were to then measure shortly after on the x-axis you would find that the spin has become indistinguishable.

that can only be observed in one of two possible states at a time. These states are named "spin-up" or "spin-down", which corresponds to the north pole pointing up or down, respectively, with regards to the axis of measurement (typically the vertical z-axis). 
%\subsubsection{}
\todo[inline]{Talk about the electron spin here}
\subsubsection{Quantum Devices}
\todo[inline]{Talk about the SET here}
A quantum device is any device that operates on the principles of quantum mechanics. An example is a \gls{set}

\cite{nuclear_spin_readout}


\cite{real_time_adaptive}
\subsection{Devices}
\subsubsection{PCIe Digitizer Card}
\todo[inline]{Talking points of the Digitizer solution, DMA, etc. etc.}
\cite{ATS9440}
%\subsubsection{FPGA/$\mu$Controller and ADC}
\todo[inline]{Talking points of the external FPGA and ADC solution, mention some particular examples of ADCs etc.}
\subsubsection{XMC}
\todo[inline]{Talking points of the integrated XMC solution, pre-built FPGA, ADCs and possibly with Auto-DMA}
